---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qeval

## Installation

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("jleechung/qeval")
```

## Usage

```{r, echo=TRUE, results = 'hide', message=FALSE, warning=FALSE}
library(qeval)

library(SummarizedExperiment)
library(ggplot2)
library(gridExtra)
```

Inputs path to files and their corresponding methods:

```{r, inputs}
gtf <- list.files(system.file('extdata', package = 'qeval'), full.names = TRUE, pattern = 'rds')
path <- list.files(system.file('extdata', package = 'qeval'), full.names = TRUE, pattern = 'test_data')
list.files(path)
methods <- c('bambu', 'nanocount', 'salmon', 'stringtie')
se <- constructSE(path, methods)
``` 

Annotate the summarized experiment:

```{r, annotate}
gtf <- readRDS(gtf)
se <- annotateSE(se, gtf)
se
``` 

For convenience:

```{r}
cdata <- colData(se)
sample_bambu <- cdata$ID[cdata$method == 'bambu']
sample_nanocount <- cdata$ID[cdata$method == 'nanocount']
sample_salmon <- cdata$ID[cdata$method == 'salmon']
sample_stringtie <- cdata$ID[cdata$method == 'stringtie']
``` 

## Visualisation

```{r, width = 6, height = 6}
plotHistogram(se, sample_bambu) 
``` 

We subset to spike-in data:

```{r}
features <- rownames(se)[!grepl('^ENST', rownames(se))] ## Spike-ins
``` 

Draw scatter plots with Spearman correlation between bambu and stringtie:

```{r, width = 24, height = 24}
rowData(se)$log.length <- log10(rowData(se)$length + 1) ## Add log-length to row data
p1 <- plotScatter(se, sample_bambu[1], sample_stringtie[1], features = features)
p2 <- plotScatter(se, sample_bambu[1], sample_stringtie[1], density = T, features = features)
p3 <- plotScatter(se, sample_bambu[1], sample_stringtie[1], density = F, features = features, annotate = 'num.exons')
p4 <- plotScatter(se, sample_bambu[1], sample_stringtie[1], density = F, features = features, annotate = 'log.length')
grid.arrange(p1, p2, p3, p4, nrow = 2, ncol = 2)

``` 

## Accuracy metrics

```{r, height = 8, width = 8}
features <- rownames(se)[!grepl('^ENST', rownames(se))] ## Spike-ins
samples <- colnames(se)
sample <- sample_bambu ## bambu 
reference <- sample_stringtie ## use stringtie as a baseline for comparison
```

Abundance recovery rate:

```{r, height = 8, width = 8}
ARR <- computeRecovery(se, sample, reference, features = features)
ARR$metrics
ARR$plot + geom_hline(yintercept = 1, linetype = 'dashed', color = 2)
``` 

Relative difference:

```{r, height = 8, width = 8}
RD <- computeDifference(se, sample, reference, features = features)
RD$metrics
RD$plot
```

Normalized root mean squared error:

```{r}
computeNRMSE(se, sample, reference, features = features)
```

## Reproducibility and consistency metrics

Reproducibility:

```{r, width = 24, height = 10}
rep1 <- computeReproducibility(se, sample_bambu, pt.alpha = 0.2)
rep1$metric
r1 <- rep1$plot + labs(title = 'bambu')

rep2 <- computeReproducibility(se, sample_stringtie, pt.alpha = 0.2)
rep2$metric
r2 <- rep2$plot + labs(title = 'stringtie')

grid.arrange(r1, r2, ncol = 2)
``` 

Consistency:

```{r, height = 8, width = 8}
samples <- c(sample_bambu, sample_stringtie)
computeConsistency(se, samples)
``` 

Resolution entropy:

```{r, height = 8, width = 8}
samples <- c(sample_bambu, sample_stringtie)
computeResEntropy(se, samples)
```

## Session Info

```{r}
sessionInfo()
```
